\section{Simulator technologies}

The project instructions has no specific requirement regarding the
implementation technologies used. This let us the choice in the language
used to simulate the chosen networking protocol.

Many implementations of Ethernet have been done in C mainly because it
is the most learned language in Computer Science course and for some
implementation for performance reasons. Therefor it seemed interesting
for us to do the simulator using other technologies.

The simulator require some interactions with the user, for the input
parameters and the output informations. As user experience matter, a
graphical and easy to use interface is a big advantage. Having a
graphical user interface will make easer performances evaluation and
statistics with automatic plotting.

The use of JavaScript for the computation part and HTML5 with CSS3
appear to be a smart choice. Those technologies are very popular nowadays
and many improvement has been done in the past year on it. The reasons
of this popularity are mainly due to the ease of use of those
technologies. Indeed every one can execute a simple script or view a web
page with it wen browser. There is no need to install many tools such as
compiler, libraries and so on. In addition, thanks to advanced
frameworks such as JQuery, development and cross-compatibility have
become much easier.
Moreover all the modern browser such as Chrome, Firefox or Internet
Explorer are evolving very quickly to support more and more features and
performances of JavaScript engine has never been so good. We
can now execute huge script in a browser without experiencing latency.

